\documentclass{article}
\usepackage{hyperref}

\begin{document}

\title{Design Specification}
\author{Team 13}
\date{\today}
\maketitle

\newpage
\tableofcontents
\newpage

\section{Project Overview}
This project is a mock Final Fantasy VII-style RPG game application. The software is designed to include a basic user interface, game logic, character actions, and turn-based battle mechanics.

\section{Pages and Parts of the Project}

\subsection{Main Menu}
The main menu allows the user to start the game, access options, or exit the application.

\subsection{Game Screen}
The game screen displays the player character, environment, and available user actions.

\subsection{Battle Screen}
The battle screen allows the player to choose attacks, view health, and interact with enemy characters.

\subsection{Inventory System}
The inventory system will store items, weapons, or other player resources.

\subsection{Save and Load System}
The save and load system will store basic player progress, character status, and game state.

\section{Tools Used}

\begin{itemize}
    \item GitHub - Repository and version control
    \item Jira - Sprint planning and task management
    \item TestRail - Test case and test run documentation
    \item LaTeX - Project documentation
    \item Docker - Container environment setup
\end{itemize}

\section{Packages, Dependencies, and Libraries}

\begin{itemize}
    \item Java Development Kit (JDK)
    \item JavaFX
    \item Git
    \item Docker
    \item Optional: JSON library for save data
\end{itemize}

\section{Docker Container Requirements}

The Docker container should include the required runtime environment for the project to run. The container may need:

\begin{itemize}
    \item Base image with Java installed
    \item JavaFX dependencies
    \item Source code copied into the container
    \item Commands to compile and run the project
\end{itemize}

\section{Future Improvements}

Future improvements may include expanded maps, additional characters, more battle options, enemy AI, save/load improvements, and a more detailed inventory system.

\end{document}