\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\geometry{margin=1in}

\title{Software Design Document \\ \large Final Project Submission: FF7 Mockup}
\author{Andres Cagungun \\ Kyle Ngo \\ Jaiden Ramirez-Gannon \\ Nicholas Siu \\ Joseph Lopez}
\date{Version 1.0 \\ May 15, 2026}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Introduction}

\subsection{Purpose}
This is a take on a traditional RPG based on Final Fantasy 7. This breaks down vital aspects of an RPG, like menus (main menu, combat menu, etc.), turn-based combat system, enemy spawn rate, reward system, character/role selection, equipment balancing, and level balancing.

\subsection{Intended Audience}
Developers, testers, instructors.

\subsection{System Overview}
A high-level overview of the RPG structure and gameplay flow.

\section{System Architecture}

\subsection{Workflow}
World $\rightarrow$ Encounter $\rightarrow$ Battle $\rightarrow$ Rewards $\rightarrow$ Return to World

\section{User Interface}

\subsection{Main Menu}
\begin{itemize}
    \item \textbf{Start Game} — Leads to save file selection.
    \item \textbf{Save Files} — Stores player progress, character status, and game state. Up to 10 save files.
    \item \textbf{Options} — Includes cheats, volume, hotkeys, etc.
    \item \textbf{Exit} — Closes the game.
\end{itemize}

\subsection{In-Game Menu}
After loading into the world, players may open a menu containing:
\begin{itemize}
    \item Continue
    \item Characters (names, descriptions, health, secondary bars, equipment)
    \item Inventory (equipment, potions, lore items)
    \item Equipment (weapons, armor, magic staves, etc.)
    \item Settings (game, display, audio)
    \item Exit to Main Menu
    \item Exit Game
\end{itemize}

\section{Glossary}
\begin{longtable}{p{0.25\linewidth} p{0.65\linewidth}}
\textbf{Term} & \textbf{Definition} \\
\hline
RPG & Role-Playing Game \\
EXP & Experience Points \\
\end{longtable}

\section{References}
None at the moment.

\end{document}
